\documentclass[line,margin]{res} 
\usepackage[hidelinks]{hyperref}
\pagestyle{plain}

\begin{document}
\moveleft.5\hoffset\centerline{\LARGE\bf Evan Lowry}
\moveleft.5\hoffset\centerline{exitiumonline.com   {$\bullet$}   Nova Scotia, Canada {$\bullet$}   lowry.e@gmail.com}
 
\begin{resume}
\section{SUMMARY}
Software Developer fluent in Python, Scala and C. Experience in all stages of
large scale web application development. Keen interest in architecture, 
application security and functional languages.

\section{SKILLS}
\textit{Languages}: C/C++, Java/Scala, Javascript/Typescript, Python, Shell, SQL \\
\textit{Frameworks}: AngularJS/Angular2, Django, PlayFramework, Pylons/Pyramid  \\
\textit{Build Tools}: Jenkins, Docker, DEB/RPM Packaging, git, svn, sbt, Gradle, Make \\
\textit{Other}: Vim, AWS, GraphViz, Spark, ArchLinux, Debian, CentOS

\section{EXPERIENCE}
\textbf{Chief Technical Officer} \hfill Mar 2015--March 2017 \\
\textit{PitchPlay Inc. Halifax, NS} \hfill \textit{Cofounder}
\begin{itemize} \itemsep-2pt
    \item Creation of real-time digital signal processing server interfaced via webRTC.
    \item Design and development of product SPA web frontend.
    \item Developed company strategy, business plan, product requirements and roadmaps.
    \item Managed small cross-functional team of employees in sales, development, and marketing.
    \item Large data processing via Apache Spark.
\end{itemize}

\textbf{Web Applications Developer} \hfill May 2012--May 2015 \\
\textit{NTT Data Inc. Halifax, NS} \hfill \textit{Consultant to Pason Systems}
\begin{itemize} \itemsep-2pt
    \item Sustaining development on a wide range of oil and gas analysis software.
    \item Development of data transport and system infrastructure services.
    \item Migrated critical legacy software to modern languages.
    \item Created software update system for managing remote oil rig upgrades.
    \item Designed and implemented a distributed rig auditing system.
    \item Led and designed implementation of CI infrastructure, deployment pipelines.
    \item Application security testing (SQLi).
\end{itemize}

\textbf{Software Developer} \hfill Oct 2010--Apr 2011 \\
\textit{Nova Scotia Community Access Program. Halifax, NS} \hfill \textit{Independant Consultant}
\begin{itemize}  \itemsep-2pt
    \item Designed and implemented a payroll and intern management system.
\end{itemize} 

\textbf{Software Developer} \hfill May 2009--Sep 2009 \\
\textit{Job Search Services. Cole Harbour, NS} \hfill \textit{Internship}
\begin{itemize} \itemsep-2pt
    \item Created a time tracker for calculating employee paid time off.
    \item Maintained public facing website.
\end{itemize}

\textbf{Software R\&D} \hfill Oct 2007--Mar 2008 \\
\textit{Liberated Learning Center. Halifax, NS} \hfill \textit{Contract}
\begin{itemize} \itemsep-2pt
    \item Created a flash based multimedia player with IBM's ViaScribe technology, providing speech-to-text transcriptions of university lectures.
    \item Researched accessibility concerns with Flash/Actionscript 3.0
    \item Submitted paper on actionscript 3.0 accessibility to ASSETS. (Not published)
\end{itemize}

\textbf{Web Developer} \hfill Jun 2007--Aug 2007 \\
\textit{Job Search Services. Cole Harbour, NS} \hfill \textit{Internship}
\begin{itemize} \itemsep-2pt
    \item Design and creation of public website.
    \item Heavy focus on web accessibility and legacy browser compatibility.
\end{itemize}
\end{resume}
\clearpage

\moveleft.5\hoffset\centerline{\LARGE\bf Evan Lowry}
\moveleft.5\hoffset\centerline{exitiumonline.com   {$\bullet$}   Nova Scotia, Canada {$\bullet$}   lowry.e@gmail.com}

\begin{resume}
\section{EDUCATION}
\textbf{Bachelor of Science}, Computer Science \hfill May 2012 \\
Saint Mary's University, Halifax, Canada \\
Minor: Psychology

\textbf{SANS SEC401}, Security Essentials\hfill Nov 2013 \\
SANS Technology Institute, OnDemand/Self Study

\section{CERTIFICATES}
\textbf{GIAC Security Essentials Certificate}, Certified Professional \hfill Nov 2013 \\
GIAC, Analyst \#34582

\section{MEMBERSHIPS}
\textbf{GIAC Advisory Board}, Member \hfill Dec 2013--Current \\
\textbf{EFF}, Supporter \hfill Jun 2013--Current \\
\textbf{IEEE}, Professional Member \hfill Sep 2014--Dec 2016 \\
\textbf{IEEE}, Signal Processing Society Member \hfill Sep 2014--Dec 2016 \\
\textbf{IEEE}, Computational Intelligence Society Member \hfill Sep 2014--Dec 2016 \\
\textbf{ACM}, Student Member \hfill Sep 2007--Mar 2012

\section{AWARDS}
ACM Style Programming Competitions
\begin{itemize} \itemsep-2pt
    \item 1st place (ACM APICS): 2007, 2010
    \item 2nd place (SMU HSPC): 2006
    \item 3rd place (SMU HSPC): 2007
    \item Top ten finishes (ACM ICPC): 2007, 2008, 2010
\end{itemize}

Hackathon Style Competitions
\begin{itemize} \itemsep-2pt
    \item Winner: Equal6's NTT Data challenge, 2012
    \item Winner: Equal6's Lixar challenge, 2012
\end{itemize}

\section{PROJECTS}
\textbf{Swan Audio} \hfill \url{https://swanaudio.com} \\
Exploring the world of audio electronics. Firmware development for various experiments. 

\textbf{JIRA IRC Resolver} \hfill \url{https://github.com/lykathia/irc-jira-d} \\
Quick learning project in the D programming language. Created to solve the issue of figuring out what
anyone was talking about when they referenced JIRA ticket numbers in chat.

\textbf{Blink1 Linux IM Status Light} \hfill \url{https://github.com/todbot/blink1} \\
Contribution to the blink1 USB light, giving a script to toggle the colour of the light based on pidgin status. \\
Available at: \href{https://github.com/todbot/blink1/blob/master/linux/contrib/pidgin-to-blink1.sh}{linux/contrib/pidgin-to-blink1.sh}

\textbf{Raytracer} \hfill \url{http://cs.smu.ca/~e_lowry/raytracer} \\
Raytracer developed for a University graphics course.
\begin{itemize} \itemsep-2pt
    \item Reflection, refraction, specular lighting, anti-aliasing
    \item Multithreading
\end{itemize}

\section{INTERESTS}
Guitar, Drums, Dungeons and Dragons, Homebrewing, Functional Programming, Security, Software Architecture

\end{resume}
\end{document}
